comparing_scenario

### 2021-01-29 comparing_scenario.Rmd
Comparing the original vs weighted data

```{r}
load("wages_hs2020.rda")
load("wages_hs2020_sc1.rda")
load("wages_hs2020_sc2.rda")
```

@@

bp_sc1 <- ggplot(wages_hs2020_sc1) +
  geom_boxplot(aes(x = mean_hourly_wage)) +
  facet_wrap(~year) +
  ggtitle("Scenario 1")

bp_sc2 <- ggplot(wages_hs2020_sc2) +
  geom_boxplot(aes(x = mean_hourly_wage)) +
  facet_wrap(~year) +
  ggtitle("Scenario 2")

bp_ori
bp_sc1
bp_sc2

@@

wages_sc2 <- as_tsibble(x = wages_hs2020_sc2,
                    key = id,
                    index = year,
                    regular = FALSE)
```

@@

wages_obs_ori <- get_obs(wages_ori)
wages_obs_sc1 <- get_obs(wages_sc1)
wages_obs_sc2 <- get_obs(wages_sc2)

nrow(wages_obs_ori)
nrow(wages_obs_sc1)
nrow(wages_obs_sc2)
```

@@

```{r}
summary(wages_sc1$mean_hourly_wage)
```

```{r}
summary(wages_sc2$mean_hourly_wage)
```

>>>>

```{r}
load("wages_hs2020.rda")
load("wages_hs2020_weighted.rda")
```

@@

bp_wei <- ggplot(wages_hs2020_weighted) +
  geom_boxplot(aes(x = mean_hourly_wage)) +
  facet_wrap(~year) +
  ggtitle("Weighted")

bp_ori
bp_wei

@@

wages_sc2 <- as_tsibble(x = wages_hs2020_sc2,
                    key = id,
                    index = year,
                    regular = FALSE)

wages_weighted <- as_tsibble(x = wages_hs2020_weighted,
                    key = id,
                    index = year,
                    regular = FALSE)
```

@@

wages_obs_ori <- get_obs(wages_ori)
wages_obs_sc1 <- get_obs(wages_sc1)
wages_obs_sc2 <- get_obs(wages_sc2)
wages_obs_weig <- get_obs(wages_weighted)

nrow(wages_obs_ori)
nrow(wages_obs_sc1)
nrow(wages_obs_sc2)
nrow(wages_obs_weig)
```

@@

```{r}
summary(wages_weighted$mean_hourly_wage)
```
